---
title: 'Visualización y Análisis en <img height="90" width="90" class="fa" src="./Image/logo/rstudio.svg"/>'
subtitle: Visualización, análisis estadístico <br> y ecológico en R
author:
- Javier Tamayo Leiva <br><a href="mailto:j.tamayo.leiva@gmail.com"><img height="30" width="30" src="./Image/logo/envelope-solid.svg"/></a> <a href="https://orcid.org/0000-0003-2610-6957"><img height="30" width="30" src="./Image/logo/orcid.svg"/></a> <a href="https://scholar.google.com/citations?user=Rr-4cmQwXX4C&hl=es"><img height="30" width="30" src="./Image/logo/google-scholar.svg"/></a> <a href="https://www.researchgate.net/profile/Javier-Tamayo"><img height="30" width="30" src="./Image/logo/researchgate.svg"/></a> <a href="https://twitter.com/TamayoLeiva_J"><img height="30" width="30" src="./Image/logo/twitter.svg"/></a> <a href="https://github.com/TamayoLeivaJ"><img height="30" width="30" src="./Image/logo/github.svg"/></a> <a href="https://www.linkedin.com/in/javier-ignacio-tamayo-leiva-94613267/"><img height="30" width="30" src="./Image/logo/linkedin.svg"/></a>
institute: "Pontificia Universidad Católica de Chile"
date: '2021'
output:
  xaringan::moon_reader:
    self_contained: true
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>`
---
<style>
.title-slide {
  background-size: 70%;
  background-position: center;
}
.fa {
  vertical-align: middle;
}
.center2 {
  margin: 0;
  position: absolute;
  top: 50%;
  left: 50%;
  -ms-transform: translate(-50%, -50%);
  transform: translate(-50%, -50%);
}
body {
  text-align: justify;
}
.title-slide h1 {
    color: #F2EAD0;
    font-size: 90px;
    font-family: "blacksword";
}
.title-slide, .title-slide h2, .title-slide h3 {
    color: #FFF9F2;
    font-family: 'Cormorant Garamond', serif;
}
.remark-slide-number {
  position: inherit;
}
.remark-slide-number .progress-bar-container {
  position: absolute;
  bottom: 0;
  height: 4px;
  display: block;
  left: 0;
  right: 0;
}
.remark-slide-number .progress-bar {
  height: 100%;
  background-color: #F2CB07;
}
.left-code {
  color: #777;
  width: 38%;
  height: 92%;
  float: left;
}
.right-plot {
  width: 60%;
  float: right;
  padding-left: 1%;
}
</style>

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=4.5, fig.height=6, fig.retina=2,
  eval = TRUE,
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2) 
library(gridExtra)
library(DiagrammeR)
library(RColorBrewer)
library(viridis)
library(xaringanthemer)
style_duo_accent(
  primary_color = "#136585",
  secondary_color = "#73455E",
  inverse_header_color = "#D7D7D9",
  title_slide_background_image = "./Image/Generative_Art_005.png",
  title_slide_text_color = "#F2F2F2",
  link_color = "#DAAB27",
  text_font_google = google_font("Roboto Slab", "400", "400i", "600i", "700"),
  header_font_google = google_font("Antonio", "300","500","700")
)
# xaringanExtra options
# Provides more obvious code highlighting. Great for teaching.
xaringanExtra::use_extra_styles(  # higlights code
  hover_code_line = TRUE,         #<<
  mute_unhighlighted_code = TRUE  #<<
)

# Turns on clipboard options. Great for giving code to students.
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "<i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
)

# Extra options.
xaringanExtra::use_tachyons()
xaringanExtra::use_fit_screen()
```
